%%%%%%%%% BOX %%%%%%%%%%%%
% this is my current "definition" environment
% \newtcolorbox[auto counter]{definitions}[1][] {
%   enhanced,
%   breakable,
%   arc=0mm,
%   title={\textbf{Box \thetcbcounter. Metrics}},
%   #1
% }

% \begin{definitions}[colback=blue!5!white,colframe=blue!75!black,label=box:metrics]

% Hello world.

% \end{definitions}
%%%%%%%%%%%%%%%%%%%%%%%%%%

% @AML: Not sure the best way to start the description of each metric. 

\newcommand{\SweepsMetricName}{
The \textbf{number of coalescence events} in a population indicates the frequency of selective sweeps.
}

\newcommand{\MutationCountMetricName}{
The number of mutations along a lineage, its \textbf{mutation count}, shows [...].
}

\newcommand{\PhenotypicVolatilityMetricName}{
\textbf{Phenotypic volatility} measures the number of instances along a lineage where an offspring has a different phenotypic profile than its parent. 
This indicates the rate at which [...].
}


\newcommand{\MutationalStabilityMetricName}{
\textbf{Mutational stability} is the proportion of mutated offspring along a lineage whose phenotypic profiles differs from that of their parent. 
Mutational stability thus examines the frequency at which mutations effect change in an offspring's phenotype. 
}

\newcommand{\TaskPerformanceMetricName}{
The \textbf{final novel task count} measures the number of unique \textit{novel} tasks performed by the most abundant genotype in the final population (ranges from 0 to 71). 
This measures the level of exploitation of the fitness landscape at a given point in time. (i.e., the mapping between genetic space and phenotype space)
}

\newcommand{\TaskDiscoveryMetricName}{
\textbf{Lineage novel task count} measures the number of unique \textit{novel} tasks performed by a given lineage, even if those tasks are later lost. 
This measures the level of exploration of the fitness landscape (i.e., the mapping between genetic space and phenotype space)
}

\newcommand{\TaskLossMetricName}{
\textbf{Lineage novel task loss} measures the number of \textit{novel} tasks that were performed by an organism in a given lineage and then lost in the organism's offspring. 
Lineage task loss measures how often a lineage fails to retain evolved traits over time and thus indicates the ability for traits to be maintained over time.
}

\newcommand{\FinalPoisonMetricName}{
The number of times the \code instruction is executed by the most abundant genotype in the final population is recorded as the \textbf{final \code{poison} count}.
This measures how effectively a population has purged deleterious mutations at given point in time. 
}

\newcommand{\LineagePoisonMetricName}{
\textbf{Lineage \code{poison} increases} measures the total number of instances along a given lineage where a mutation causes an offspring to execute the \code{poison} instruction more times than its parent. 
This indicates how often deleterious hitchhiking occurred along the lineage.
}

\newcommand*{\thead}[1]{\multicolumn{1}{c}{\bfseries #1}}

\setlength{\tabcolsep}{16pt}
\renewcommand{\arraystretch}{1.5}
\begin{table}[h]
    \centering
    
    \rowcolors{2}{gray!25}{white}
    \begin{tabularx}{\linewidth}{X} % p{10cm}
        \rowcolor{gray!50}
        \hline 
        \thead{Definitions} \\ % & \thead{Description}   \\
        \hline
        \SweepsMetricName \\ % & \SweepsMetricDesc \\
        \MutationCountMetricName \\ %& \MutationCountMetricDesc \\
        \PhenotypicVolatilityMetricName \\ %& \PhenotypicVolatilityMetricDesc \\
        \MutationalStabilityMetricName \\ %& \MutationalStabilityMetricDesc \\
        % (architecture metric(s)) & \\
        \TaskPerformanceMetricName \\ %& \TaskPerformanceMetricDesc \\
        \TaskDiscoveryMetricName \\ %& \TaskDiscoveryMetricDesc \\
        \TaskLossMetricName \\ %& \TaskLossMetricDesc \\
        \FinalPoisonMetricName \\ %& \FinalPoisonMetricDesc \\
        \LineagePoisonMetricName \\ %& \LineagePoisonMetricDesc \\
        \hline
    \end{tabularx}
    
    \caption{\textbf{Metric descriptions.}}
    \label{tab:metrics-definitions}
\end{table}

%     \item number of coalescence events
%     \item mutation count
%     \item phenotypic volatility
%     \item mutational stability
%     \item [architecture metric(s)]
%     \item final task count
%     \item lineage task count
%     \item lineage task loss
%     \item final poison count
%     \item lineage poison count

% \newcommand{\DecOwnRegulatorName}{\code{DecOwnRegulator}}
% \newcommand{\DecOwnRegulatorDescription}{Subtract one from the regulatory modifier of the currently executing module.}


